---
title: "Group 41 CA pollution burden"
author: "Sachiko Lamen, Chase Tarr"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

## Read in data and clean names
```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>%
  clean_names()
```

## Creating a Scatterplot Graph
```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + 
  scale_fill_gradient(low = "mediumorchid4", high = "turquoise1") +
  theme_minimal() +
  labs(x = "Percent White",
       y = "CalEnviroScreen 3.0 Score", caption = expression(paste(bold("Figure 1:"), "High CalEnviroScreen3.0 scores indicate high cumulative pollution burdens. Each hexagon and it's corresponding fill color represents the number of census tracts at each value."))) +
   theme(plot.caption = element_text(hjust = 0.5))
```
An *increase* in the percentage of white of a population correlates with a lower CalEnviroScreen3.0 score. This indicates a lower pollution burden and decreased socioeconomic vulnerabilities in communities with higher white populations. Communities with a white population between **0%** and **25%** generally receive higher CES 3.0 scores (reaching levels of up to 75) while communities with a white population percentage above **75%** are likely to receive lower CES 3.0. This indicates that there is a *negative correlation* between CES 3.0 scores and increased white population.
