---
title: "Group 41 CA pollution burden"
author: "Sachiko Lamen, Chase Tarr"
date: "11/16/2021"
output: html_document
---
## Overview
This data, known as the CalEnviroScreen 3.0, is an Environmental Community Health Screening Tool focusing on pollution burden and socioeconomic vulnerabilities in communities. This is cross evaluated with populations of race to determine if communities with a higher percentage of white individuals experience less pollution and socioeconomic vulnerability. Higher CalEnviroScreen scores indicate high pollution burdens and vulnerable population characterstics. 
**Citation:** https://caleja.org/wp-content/uploads/2015/09/CES3.0-5.pdf
```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

## Read in data and clean names
```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>%
  clean_names()
```

## Creating a Scatterplot Graph
```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) +
  geom_hex() + 
  scale_fill_gradient(low = "mediumorchid4", high = "turquoise1") +
  theme_minimal() +
  labs(x = "Percent White",
       y = "CalEnviroScreen 3.0 Score",
       title = "CalEnviroscreen 3.0 score comparison to percent white population") +
   theme(plot.caption = element_text(hjust = 0.5)) +
  theme(panel.background = element_rect(fill = 'orange'),
          panel.grid.major = element_line(color = 'red', linetype = 'dotted'),
          panel.grid.minor = element_line(color = 'green', size = 0.5)) +
  theme(text = element_text(family="Times", size=16))
```

**Figure 1** High CalEnviroScreen3.0 (CES3.0) scores indicate high cumulative pollution burdens. Each hexagon and it's corresponding fill color represents the number of census tracts at each value.


There appears to be a *negative correlation* between percent white population and CalEnviroScreen3.0 (CES3.0) scores. We see CES3.0 scores that indicate a lower pollution burden and decreased socioeconomic vulnerabilities in communities with higher white populations. Communities with a white population between 0% and 25% generally receive higher CES 3.0 scores while communities with a white population percentage above 50% are more likely to receive lower CES 3.0 scores. 